\documentclass{article}

\begin{document}

\title{Responsibilities of an ACM Treasurer}
\date{Dec 20th, 2015}
\maketitle

\begin{flushleft}
A treasurer should budget expenditures, fill out reimbursement forms after spending money and make sure we spend all the money allotted to the club. Below I will go into detail about each of these tasks: 
\end{flushleft}

\begin{enumerate}
	\item Budget expenditures
	\begin{enumerate}
		\item Document expenditures by account on an spreadsheet. 
		\item We have two accounts that need to be kept track of \textbf{AEC} and \textbf{USG}.
		\item \textbf{Note that certain things won't be reimbursed by AEC and USG, so before making a purchase ask AEC/USG directly if the item is allowed for reimbursements.} Food is usually fine. 
	\end{enumerate}
	\item Submit reimbursements
	\begin{enumerate}
		\item Collect the following things:
		\begin{enumerate}  
			\item Any relevant \textbf{receipts with a date} of the purchase
			\item Bank statements showing the amount spent and \textbf{the name of the person who made the purchase} 
			\item Proof that the event is real with either event flyers or event signup, \textbf{if the purchase was for an event}
			\item Minutes stating that all members agreed on the purchase
			\item Small statement about how the money was/will be used and how it helped the club and/or event
		\end{enumerate}
		\item Decide which account you want to get the reimbursement from (AEC or USG) and fill out the appropriate form. Don't forget that each account will only reimburse certain things - it's always good to ask them directly what they will fund before purchasing.
		\item \textbf{Make sure you do this soon after the money is spent.} Preferably a few days after just in case there are any errors. \textbf{The business office will contact the person who submitted the form if there are errors and ask for it to be resubmitted.}
		\item AEC forms go to Jason Wallace in NAC 1/210-B and USG forms go to (I think) NAC 1/210.  
	\end{enumerate}
	\item Spend all the money or else future funding will be cut!
	
\end{enumerate}

\end{document}	